\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-01 letter.tex
add paragraph on one-sided break (E9) to letter

>>>>

Editor's point $\#9$: I have added the move of nature that determines whether the legislature gets the opportunity to the extensive form and to the discussion of the timing in the initial discussion of the model (Section 2.1: The Basic Setup). I have gathered all relevant discussion in this section as suggested.
